Kalman tracking and parameter estimation of continuous gravitational waves with a pulsar timing array

### 2023-10-29 docs/manuscript/paper.tex
add pp plot script

 This stems from the bias noted in Section \ref{sec:multiple_noise}; the posteriors inferred for these parameters are generally narrow, but are systematically biased away from the true injection values.

 Consequently the

@@

 This translates in the PP plot to posteriors which are too narrow to contain the injected value within the credible interval. The origin of the bias is discussed in Section \ref{sec:bias}.

>>>>

 This stems from the bias noted in Section \ref{sec:multiple_noise};

\textbf{ NEW DATA INCOMING. See OCT pp}

 the posteriors inferred for these parameters are generally narrow, but are systematically biased away from the true injection values.

 Consequently at higher-value credible intervals the posterior is too narrow to

@@

 This translates in the PP plot to posteriors which are too narrow to contain the injected value within the credible interval.

 The origin of the bias is discussed in Section \ref{sec:bias}.
